---
title: "Developing Data Products Week 4 Assignment"
author: "Umesh Moolchandani"
date: "May 15 2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(nloptr)
```

## Reproducible Pitch

This peer assessed assignment has two parts. First, create a Shiny application and deploy it on Rstudio's servers. Second, use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

The shiny application prepared in this assignment can be found at:

https://moolchandani.shinyapps.io/shiny_assignment


The source codes of server.R and ui.R can be found at:

https://github.com/moolchandani/developing-data-products-week4-assignment


## Overview {.smaller}

The shiny app plots graph against miles per gallon (mpg) for different variables from the mtcars dataset.


```{r, echo = TRUE}
head(mtcars)
```

## Regression Model Analysis {.smaller}
We'll build linear regression models based on different variables and try to find out the best model fit and compare it with the base model. 

```{r echo = TRUE}
summary(mtcars)
```

## UI Code {.smaller}

The ui.R code can be found at:

### Sample Code

```{r, eval=FALSE, echo=TRUE}
library(shiny)

shinyUI(
  navbarPage("Cars Data - Prediction of mpg using Regression Analysis",
             tabPanel("Simple Regression",
                      (fluidPage(
                        titlePanel("Predicting Miles per Gallon (mpg) with Simple Regression Models"),
                        sidebarLayout(
                          sidebarPanel(
                            selectInput("variable", "Select Input for Simple Regression",
                                        c("am","cyl","hp","wt","disp","drat","qsec","gear","carb")),
                            checkboxInput("simple_model","Show Simple Model",value=FALSE),
                            submitButton("Submit")
                            
                            
                          ),
                          mainPanel(
                            h3("Simple Regression Model"),
                            textOutput("model"),
                            tabsetPanel(type = "tabs", 
                                        tabPanel("BoxPlot", plotOutput("simpleboxplot"),textOutput("simpletext")),
                                        tabPanel("Summary", verbatimTextOutput("simplesummary")),
                                        tabPanel("Residual Plots", plotOutput("simpleresidual"))
                                        
                                        
                                        
                            )
                          )
                        )
                        
                      ))),
             
             tabPanel("Multivariable Regression (Full)",
                      fluidPage(
                        titlePanel("Regression with All Variables for mpg Prediction"),
                        sidebarLayout(
                          sidebarPanel(
                            checkboxInput("multimodel","show full regression model",value=FALSE),
                            submitButton("Submit")
                          ),
                          mainPanel(
                            h3("Multivariable Regression Model"),
                            textOutput("fullmodel"),
                            tabsetPanel(type = "tabs", 
                                        
                                        tabPanel("Summary Full", verbatimTextOutput("multisummary")),
                                        tabPanel("Residual Plots Full", plotOutput("multiresidual"))
    
                            )
                            
                          )
                        )
                      )
                      
             ),
             tabPanel("Multivariable Regression (Features Selection)",
                      fluidPage(
                        titlePanel("Regression with Best Variables for mpg Prediction"),
                        sidebarLayout(
                          sidebarPanel(
                            checkboxInput("show","Show/Hide Best Variable Subsets",value = FALSE),
                            checkboxInput("variablenum","Show/Hide Best Variable Number",value = FALSE),
                            checkboxInput("variables","Show/Hide Best Variables",value = FALSE),
                            
                            submitButton("Submit")
                            
                            
                          ),
                          mainPanel(
                            h3("Best Subset Regression Model"),
                            verbatimTextOutput("bestvariablesubsets"),
                            verbatimTextOutput("variablenumber"),
                            verbatimTextOutput("bestvariables"),
                            
                            tabsetPanel(type = "tabs", 
                                        
                                        tabPanel("Summary ", verbatimTextOutput("multisummary2")),
                                        tabPanel("Residual Plots", plotOutput("multiresidual2"))
                                        
                                        
                                        
                            )
                            
                          )
                        )
                      )
                      
             )
             
  ))
```


## Server Code {.smaller}

The server.R code can be found at:

### Sample Code

```{r, eval=FALSE, echo=TRUE}
library(shiny)
library(ggplot2)
library(olsrr)
data(mtcars)

mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
mtcars$am <- factor(mtcars$am,labels=c("Automatic","Manual"))

shinyServer(function(input, output) {
  
  full_model<-lm(mpg ~ am+cyl+hp+wt+disp+hp+drat+qsec+gear+carb,data=mtcars)
  best_model<-lm(mpg ~ am+hp+wt+disp+qsec,data=mtcars)
  
  formula<-reactive({
    paste("mpg ~", input$variable)
    
  })
  fit_simple<-reactive({
    lm(as.formula(formula()),data=mtcars)
  })
  
  output$model<-renderText({
    if(input$simple_model)
    {formula()}
  })
  
  
  
  output$simpleboxplot <- renderPlot({
    # check for the input variable
    if (input$variable == "am") {
      # am
      mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]], labels = c("Automatic", "Manual")))
      p <- ggplot(mpgData, aes(var, mpg,fill=var)) + 
        geom_boxplot(alpha=0.3) + 
        xlab(input$variable)
      print(p)
      
    }
    else if(input$variable == "cyl"|input$variable == "vs"|input$variable == "gear"|input$variable == "carb"){
      # cyl and gear
      mpgData <- data.frame(mpg = mtcars$mpg, var = factor(mtcars[[input$variable]]))
      p <- ggplot(mpgData, aes(var, mpg,fill=var)) + 
        geom_boxplot(alpha=0.3) + 
        xlab(input$variable)
      print(p)
      
    }
    else{
      output$simpletext<-renderText({
        
        
        if (input$variable!= "am"|input$variable != "cyl"|input$variable!= "vs"|input$variable!= "gear"|input$variable!= "carb"){
          
          print("We don't have a categorical grouping variable!")
        }
        
      })
      
    }
    
  })
  
  
  output$simplesummary<-renderPrint({
    summary(fit_simple())
  })
  
  
  output$simpleresidual<-renderPlot({
    
    par(mfrow = c(2, 2), bg="pink")
    plot(fit_simple())
  })
  
  
  
  output$multisummary<-renderPrint({
    summary(full_model)
    
    
  })
  
  output$multiresidual<-renderPlot({
    
    par(mfrow = c(2, 2), bg="pink")
    plot(full_model)
  })
  
  output$bestvariablesubsets<-renderPrint({
    
    if(input$show)
    {ols_step_best_subset(full_model,details=TRUE)}
    else{"Check Show Hide Best Variable Subsets and Press Submit Button"}
    
  })
  
  output$fullmodel<-renderText({
    
    if(input$multimodel)
    {print("mpg ~ am+cyl+hp+wt+disp+hp+drat+qsec+gear+carb")}
  })
  
  output$variablenumber<-renderPrint({
    
    if(input$variablenum)
    {adjr<-ols_step_best_subset(fit_multivariable_full,details = TRUE)$adjr
    which(adjr==max(adjr))}
    else{"Check Show Hide Best Variable Number and Press Submit Button"}
    
  })
  
  output$bestvariables<-renderPrint({
    
    if(input$variables)
    {
      adjr<-ols_step_best_subset(fit_multivariable_full,details = TRUE)$adjr
      var<-ols_step_best_subset(fit_multivariable_full,details = TRUE)$predictors[which(adjr==max(adjr))]
      print(var)
    }
    else{"Check Show Hide Best Variables and Press Submit Button"}
    
  })
  
  
  output$multisummary2<-renderPrint({
    summary(best_model)
    
    
  })
  output$multiresidual2<-renderPlot({
    
    par(mfrow = c(2, 2), bg="pink")
    plot(best_model)
  })
})

```

